% vim: set tw=78 sts=2 sw=2 ts=8 aw et ai:

Virtually all connection oriented communication in the Internet is done using TCP. It provides reliability, ordering and error-checking mechanisms together with the capability to adapt to network conditions in order to ensure swift and correct delivery of data between the communicating endpoints. However, TCP has been designed to use a single link and follow a single path between two IP addresses that cannot be changed without ending the layer 4 connection. Today, devices have evolved to have multiple network interfaces and the need arose for a protocol that would make full use of all the network resources in order to maximize throughput, improve reaction to failures and even optimize energy consumption. 

MPTCP is the IETF's attempt to address the need mentioned above. The specification was published as an Experimental standard in RFC 6824 and a stable Linux kernel implementation is also available, although it has not been upstreamed as of the time of writing. In order to be effective as a TCP replacement, MPTCP needs to satisfy three conditions: be backwards compatible with TCP (current applications need to be able to run unmodified on MPTCP), be compatible with today's networks (run on existing devices) and perform at least as well as TCP in any given situation. It has two obvious main use cases: mobile devices which are equipped with both WiFi and 3G interfaces and datacenters, where it can improve robustness.

MPTCP works by establishing multiple subflows under a single socket
connection, with each subflow able to take a separate path to the destination.
Subflows are established using TCP SYN packets with special MPTCP options. The
SYN contains the MP_CAPABLE option which must be echoed in the SYN/ACK which
is received from the other end. MPTCP always falls back on TCP if this
negotiation cannot be completed. Each subflow can be seen as a TCP flow
independently. Subflows have their own sequence numbers for handling
retransmissions, while there is also a per-connection sequence number mechanism
to ensure reordering at the destination. MPTCP's break-before-make mechanism
allows subflows to be created or destroyed while keeping the connection alive
with everything being transparent to the application i.e. switching to another
network interface with a different IP address.

The main obstacle for large scale deployment of MPTCP is the presence of
middleboxes, intermediary routers or other network devices that interfere and
modify packets that pass through them. Since MPTCP relies on newly created TCP
options, this is a major issue. MPTCP researchers have found that up to 6\% of
middleboxes strip unkown options from the TCP header (with that percentage
increasing to 14\% when dealing with connections on port 80)
\cite{how-hard-can-it-be}. Middlebox constraints have also influenced other
design decisions for MPTCP, such as additional subflows in an existing
connection requiring a SYN handshake because NAT devices and firewalls drop
packets that are not preceded by a SYN.

Still, the major constraint for MPTCP remains performing at least as well as TCP in any conditions. Since MPTCP can use multiple types of interfaces, each with different characteristics, there is the need to understand how connection or subflow parameters can affect performance.

The purpose of the initial phase of our project is to build a simulation environment and use it to vary different TCP communication parameters and channel conditions in order to observe how MPTCP performance is affected. We experiment with parameters such as:
\begin{itemize}
\item Bandwidth. Since the tests are run inside a simulator, we are able to test traffic behavior over links ranging from very low bandwidth to very high.
\item Delay. Similar to bandwidth, we can manipulate delay in order to observe how MPTCP adapts to different RTT values on different paths.
\item Loss. Channel loss greater than 10\% has been found to cause MPTCP to
perform 20-30\% worse than TCP because the congestion controller overestimates
the throughput of such subflows \cite{how-hard-can-it-be}. We further investigate on this matter.
\item Receive buffer. The size of the receive buffer is related to the amount
of data in flight and there is the need for a compromise between using too
much system memory and using the channel inefficiently.
\item Initial congestion window. MPTCP uses per-subflow congestion windows.
We wish the observe the correlation between the initial congestion window
size and the bandwidth-delay product.
\end{itemize}
